Resource Buying Games

### 2017-03-02 paper.tex
unweighted game

\section{Congestion Model}
In this section we want to introduce a structure to model resources and demands
of actors on resources. Therefore, we consider a set of players $N$ and a set
of resources $E$. Every player has a personal aim which can be achieved by
different resources. This is modelled for a player $i\in N$ as family
$\mathcal{S}_{i}$ of sets $S_{i}\subseteq E$ of resources. Additionally, we
want to account for different demands of players on resources by fixing a
demand for every player $i$ as $d_{i}\in\mathbb{N}$. Finally, the cost of a
resource depends on the load the players put onto the resource modelled as
individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{N}$ for every
resource $e\in E$. As an example consider different actors that build a shared
network infrastructure. The connections in the network are resources, the
actors are the players which have individual spots they want to connect.
Different actors might need different bandwidth for connections, i.e. their
demands, and the cost for using connections depends on the used bandwidth.
Accordingly we obtain a congestion model
\begin{equation*}
  \mathcal{M} = \tupel{N, E, \mathcal{S} = \times_{i\in N}\mathcal{S}_{i},
  (d_{i})_{i\in N}, (c_{e})_{e\in E}}
\end{equation*}
for which we introduce some additional definitions:
\begin{itemize}
  \item for a profile $S\in\mathcal{S}$ we define
    the demand on resource $e$ for $S$ as
    $\ell(S) = \sum_{i\in N:e\in S_{i}}d_{i}$
  \item we lift $c_{e}$ to the set $\mathcal{S}$ by setting
    $c_{e}(S) = c_{e}(\ell_{e}(S))$ for $S\in\mathcal{S}$
\end{itemize}

The cost that results from a profile $S\in\mathcal{S}$ is covered by all
players. To model this we consider the game 
\begin{equation*}
  G = \tupel{N, \mathcal{S}\times\mathcal{P}, \pi}
\end{equation*}
where $\mathcal{P} = \times_{i\in N}\mathcal{P}_{i}$ and
$\mathcal{P}_{i} = |\mathbb{R}_{+}^{|E|}|$ to model how much every player
contributes in paying for the cost of every resource. We denote the element
from $\mathcal{P}_{i}$ for $e\in E$ with $p_{i}^{e}$ and call $e\in E$ bought
under $\tupel{S, p}\in \mathcal{S}\times\mathcal{P}$ if
$c_{e}(S)\leq \sum_{i\in N}p_{i}^{e}$. The function $\pi$ gives the payoff for
every player for a strategy profile $\tupel{S, p}$ by
\begin{equation*}
  \pi_{i}(S, p) = \begin{cases}
    \sum_{e\in E}p_{i}^{e} &\text{ if $S_{i}$ is bought under
    $\tupel{S, p}$ (i.e. all $e\in S_{i}$ are bought)}\\
    \infty &\text{ otherwise}
  \end{cases}
\end{equation*}
Thus, every player tries to minimise her personal contribution to the costs
but ensures that her demand is satisfied.
\section{Matroids}
In this section we present the combinatorial structure of Matroids.
\todo{why matroids?}

@@

\section{Unweighted Matroid Games}

>>>>

\section{Congestion Model}
In this section we want to introduce a structure to model resources and demands
of actors on resources. Therefore, we consider a set of players $N$ and a set
of resources $E$. Every player has a personal aim which can be achieved by
different resources. This is modelled for a player $i\in N$ as family
$\mathcal{S}_{i}$ of sets $S_{i}\subseteq E$ of resources. Additionally, we
want to account for different demands of players on resources by fixing a
demand for every player $i$ as $d_{i}\in\mathbb{N}$. Finally, the cost of a
resource depends on the load the players put onto the resource modelled as
individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{R}_{+}$ for
every resource $e\in E$. As an example consider different actors that build a
shared network infrastructure. The connections in the network are resources,
the actors are the players which have individual spots they want to connect.
Different actors might need different bandwidth for connections, i.e. their
demands, and the cost for using connections depends on the used bandwidth.
Accordingly we obtain a congestion model
\begin{equation*}
  \mathcal{M} = \tupel{N, E, \mathcal{S} = \times_{i\in N}\mathcal{S}_{i},
  (d_{i})_{i\in N}, (c_{e})_{e\in E}}
\end{equation*}
for which we introduce some additional definitions:
\begin{itemize}
  \item for a profile $S\in\mathcal{S}$ we define
    the demand on resource $e$ for $S$ as
    $\ell(S) = \sum_{i\in N:e\in S_{i}}d_{i}$
  \item we lift $c_{e}$ to the set $\mathcal{S}$ by setting
    $c_{e}(S) = c_{e}(\ell_{e}(S))$ for $S\in\mathcal{S}$
  \item we call $c_{e}$ \emph{marginally non-increasing} if
    $c_{e}(y + \delta) - c_{e}(y) \leq c_{e}(x + \delta) - c_{e}(x)$ holds
    for all $x,y,\delta\in N$ with $x\leq y$
  \item analogously $c_{e}$ is \emph{marginally non-decreasing} if
    $c_{e}(y + \delta) - c_{e}(y) \geq c_{e}(x + \delta) - c_{e}(x)$ holds
    for all $x,y,\delta\in N$ with $x\leq y$
\end{itemize}
Note that linear and constant cost functions are marginally non-increasing.

The cost that results from a profile $S\in\mathcal{S}$ is covered by all
players. To model this we consider the resource buying game 
\begin{equation*}
  G = \tupel{N, \mathcal{S}\times\mathcal{P}, \pi}
\end{equation*}
where $\mathcal{P} = \times_{i\in N}\mathcal{P}_{i}$ and
$\mathcal{P}_{i} = |\mathbb{R}_{+}^{|E|}|$ to model how much every player
contributes in paying for the cost of every resource. We denote the element
from $\mathcal{P}_{i}$ for $e\in E$ with $p_{i}^{e}$ and call $e\in E$ bought
under $\tupel{S, p}\in \mathcal{S}\times\mathcal{P}$ if
$c_{e}(S)\leq \sum_{i\in N}p_{i}^{e}$. The function $\pi$ gives the payoff for
every player for a strategy profile $\tupel{S, p}$ by
\begin{equation*}
  \pi_{i}(S, p) = \begin{cases}
    \sum_{e\in E}p_{i}^{e} &\text{ if $S_{i}$ is bought under
    $\tupel{S, p}$ (i.e. all $e\in S_{i}$ are bought)}\\
    \infty &\text{ otherwise}
  \end{cases}
\end{equation*}
Thus, every player tries to minimise her personal contribution to the costs
but ensures that her demand is satisfied.
\section{Matroids}
In this section we present the combinatorial structure of Matroids.
\todo{why matroids?}

@@

\section{Unweighted Matroid Games with marginally non-increasing cost
functions}
We present an algorithm which computes pure Nash equilibria in unweighted
matroid games with marginally non-increasing cost functions. Firstly, an
unweighted matroid game builds upon a congestion model of the form
$\tupel{N, E, \mathcal{B} = \times_{i\in N}\mathcal{B}_{i},
(d_{i})_{i\in N}, (c_{e})_{e\in E}}$ where for all $i\in N$ holds $d_{i} = 1$
(unweighted) and every $\mathcal{B}_{i}$ is the set of bases for some matroid
$\mathcal{M}_{i} = \tupel{E_{i}, \mathcal{B}_{i}}$. The set of resources is
given by the matroids of the players $E = \bigcup_{i\in N}E_{i}$ and all cost
functions $c_{e}$ are marginally non-increasing. The algorithm
we present in the following chooses a basis for every player by iteratively
adding one element from a cut and contracting the matroid to the added element
while deleting all other elements from the cut. Since cuts are inclusion-wise
minimal deleting all but one element from one cut leaves at least one possible
basis for the player available.
